Subjective Experience of Demands and Resources across O*NET Job Elements

### 2024-04-09 Submission.Rmd
desktop push so Alicia has most recent

abstract: |
  Much of our understanding of job demands and resources rests on an assumption that some aspects of jobs are resources and some are demands. This study documents the degree of variability in subjective ratings of job characteristics with respect to interpretation as resource and demand. Next, we quantify the degree to which perceptions match the literature-implicated resources/demands of job characteristics and also document associations with stress, burnout, and engagement. Job characteristics were not commonly categorized as solely resource or demand. Rather, job resources were also frequently viewed as challenging demands. OUTCOME VARIABLE INFORMATION HERE. These findings have implications for job design and administration - resource-laden elements may also be interpreted by workers as demands.

@@

csl               : "apa7.csl"
#documentclass     : "apa7" #interact
classoption       : "jou"
#output            : "word_document"
output            : papaja::apa6_pdf

@@

+ Challenge-hindrance framework
  + Cavanaugh (~2000)
  + Last 20 years' research (variance - look at Pindek et al, 2024)
  + Appraisals

+ Antecedents (job elements)
  a. O\*Net - comprehensive
III. Consequences (outcomes)
  a. Moderation
IV. Contribution
  a. include resources

While we have accumulated a vast literature on how job demands and resources relate to and influence key organizational outcomes, recent work has called into question some of our basic assumptions regarding the experience of demands in particular. We build on the work of a small, but growing number of researchers who argue that the work elements may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges], with primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) *are there characteristics that are more likely to vary across demand and resource*, and 3) explore whether these subjective appraisals are differentially related to positive and negative outcomes. We utilize the O\*Net database (https://www.onetcenter.org/content.html), which is the primary source of occupational information in the US, and as such, provides a rich source of information about occupational requirements (i.e., work activities and context) that may be rated in terms of level of demand or resource. We will refer to these as elements of working conditions throughout this paper (e.g., personal, contextual, or task-related conditions or elements of one's work).

## The Job Demands-Resources Theory and Challenge-hindrance Stressor Framework

Two related theories serve as the foundation for the current study: @demerouti2001job's job demands-resources theory and @cavanaugh2000empirical's later challenge-hindrance stressor framework. The job demands-resources model @demerouti2001job,  @bakker2017job highlights the importance of work characteristics on the experience of motivation and strain as well as other, more distal outcomes. The job demands-resources theory distinguishes between resources and demands. *Resources* include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job]. In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is commonly cited as a demand; @demerouti2001job). The perception of an element of one’s job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; @bakker2014job).

In response to inconsistent findings regarding demands and outcomes, @cavanaugh2000empirical expanded the job demands-resources theory in proposing the challenge-hindrance stressor framework, which draws from @lazarus1984stress's work on stress and coping. The challenge-hindrance stressor framework distinguishes between *two forms of demands* -- *challenges* and *hindrances*. Both are considered stressors [e.g., @cavanaugh2000empirical]. Challenge demands promote mastery, personal growth, and future gains – these stressors should lead to coping strategies that facilitate achievement. Work characteristics consistent with this definition include time pressure and responsibility. Hindrance demands, in contrast, inhibit growth, learning and goal achievement. Hindrance stressors in a work context include role conflict, role ambiguity, and organizational politics.

@@

The original work on this topic suggests that challenge stressors are typically associated with positive outcomes and hindrance stressors are associated with negative outcomes [e.g., @cavanaugh2000empirical]. Meta-analytic explorations of this the challenge-hindrance stressor framework have generally been supportive of the framework's propositions (e.g., performance; [@lepine2005meta] and engagement, [@crawford2010linking]). @lepine2022challenge explain the mechanisms by which demands are related to performance and wellbeing outcomes. First, stressors appraised as challenges typically result in a challenge appraisal, and engagement is likely to happen as a result. Engagement, in turn, is positively related to motivation, performance, growth, and wellbeing. Of note is that this energy may be depleted eventually, leading to strain. Stressors appraised as hindrances elicit a different process. Disengagement is likely to result from a hindrance appraisal, which in contrast, negatively impacts motivation, performance, growth and wellbeing. This happens because resources are depleted via frustrations and other affectively negative reactions [@lepine2022challenge]. Recent work affirms this appraisal process. @pindek2024dynamic meta-analyzed diary studies of dynamic stressors (i.e., short-term daily experiences of stressors) and concluded that daily challenge stressors had a postive direct association with performance, but a negative indirect association with performance through strain (as described by @lepine2022challenge above). As expected, hindrance stressors had both a direct and indirect (through strain) association with performance [@pindek2024dynamic].

>>>>

abstract: |
  Much of our understanding of job demands and resources rests on an assumption that some aspects of jobs are resources and some are demands. This study documents the degree of variability in subjective ratings of job characteristics with respect to interpretation as resource and demand. Next, we quantify the degree to which perceptions match the literature-implicated resources/demands of job characteristics and also document associations with stress, burnout, and engagement. Job characteristics were not commonly categorized as solely resource or demand. Rather, job resources were also frequently viewed as challenging demands. OUTCOME VARIABLE INFORMATION HERE. These findings have implications for job design and administration particularly with regard to resource-laden elements that may also be experienced as demanding.

@@

csl               : "apa7.csl"
documentclass     : "apa7" #interact
classoption       : "jou"
#output            : "word_document"
output            : papaja::apa6_pdf

@@

I. Challenge-hindrance framework
  + Cavanaugh (~2000)
  + Last 20 years' research (variance - look at Pindek et al, 2024)
  + Appraisals [^JDR]

[^JDR]: Ignore JD theory terminology - only talk about JDR *model*, otherwise the verbage becomes confused (4/6/24)

II. Antecedents (job elements)
  a. O\*Net - comprehensive
III. Consequences (outcomes)
  a. Moderation
IV. Contribution
  a. include resources

While we have accumulated a vast literature on how job demands and resources relate to and influence key organizational outcomes, recent work has called into question some of our basic assumptions regarding the experience of demands in particular. We build on the work of a small, but growing number of researchers who argue that work elements may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges]. Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) some characteristics are more likely than others to vary across demand and resource, and 3) subjective appraisals are differentially related to positive and negative outcomes. To illuminate these questions, we consult the [O\*Net database](https://www.onetcenter.org/content.html), which provides a rich source of information about occupational requirements (i.e., work activities and context). We retain O\*Net terminology of working condition elements throughout this paper (e.g., personal, contextual, or task-related conditions or elements of one's work).

## The Job Demands-Resources Theory and Challenge-Hindrance Stressor Framework

Two related theories serve as the foundation for the current study: @demerouti2001job's job demands-resources theory and @cavanaugh2000empirical's challenge-hindrance stressor framework. The job demands-resources model [@demerouti2001job] highlights the importance of demands and resources on the experience of motivation and strain as well as other, more distal outcomes. *Resources* include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job]. In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is commonly cited as a demand; @demerouti2001job). The perception of an element of one’s job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; @bakker2014job).

In response to inconsistent findings regarding demanding work characteristics and outcomes, @cavanaugh2000empirical proposed a challenge-hindrance stressor framework, which draws from @lazarus1984stress's perspective on stress and coping. The challenge-hindrance stressor framework distinguishes between *two forms* of demands -- *challenges* and *hindrances*. Both are considered stressors [e.g., @cavanaugh2000empirical]. Challenge demands promote mastery, personal growth, and future gains – these stressors should lead to coping strategies that facilitate achievement. Work characteristics consistent with this definition include time pressure and responsibility. Hindrance demands, in contrast, inhibit growth, learning and goal achievement. Hindrance stressors in a work context include role conflict, role ambiguity, and organizational politics.

@@

The original work on this topic suggests that challenge stressors are typically associated with positive outcomes and hindrance stressors are associated with negative outcomes [e.g., @cavanaugh2000empirical]. Meta-analytic explorations of this the challenge-hindrance stressor framework have generally been supportive of the framework's propositions (e.g., performance; [@lepine2005meta] and engagement, [@crawford2010linking]). @lepine2022challenge explain the mechanisms by which demands are related to performance and wellbeing outcomes.

First, stressors appraised as challenges typically result in a challenge appraisal, and engagement is likely to happen as a result. Engagement, in turn, is positively related to motivation, performance, growth, and wellbeing. Of note is that this energy may be depleted eventually, leading to strain. Stressors appraised as hindrances elicit a different process. Disengagement is likely to result from a hindrance appraisal, which in contrast, negatively impacts motivation, performance, growth and wellbeing. This happens because resources are depleted via frustrations and other affectively negative reactions [@lepine2022challenge]. Recent work affirms this appraisal process. @pindek2024dynamic meta-analyzed diary studies of dynamic stressors (i.e., short-term daily experiences of stressors) and concluded that daily challenge stressors had a postive direct association with performance, but a negative indirect association with performance through strain (as described by @lepine2022challenge above). As expected, hindrance stressors had both a direct and indirect (through strain) association with performance [@pindek2024dynamic].

### 2024-04-09 Submission.tex
desktop push so Alicia has most recent

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  jou,mask]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\abstract{%
Much of our understanding of job demands and resources rests on an assumption that some aspects of jobs are resources and some are demands. This study documents the degree of variability in subjective ratings of job characteristics with respect to interpretation as resource and demand. Next, we quantify the degree to which perceptions match the literature-implicated resources/demands of job characteristics and also document associations with stress, burnout, and engagement. Job characteristics were not commonly categorized as solely resource or demand. Rather, job resources were also frequently viewed as challenging demands. OUTCOME VARIABLE INFORMATION HERE. These findings have implications for job design and administration - resource-laden elements may also be interpreted by workers as demands.
}

@@

\begin{itemize}
\tightlist
\item
  Challenge-hindrance framework

  \begin{itemize}
  \tightlist
  \item
    Cavanaugh (\textasciitilde2000)
  \item
    Last 20 years' research (variance - look at Pindek et al, 2024)
  \item
    Appraisals
  \end{itemize}
\item
  Antecedents (job elements)

  \begin{enumerate}
  \def\labelenumi{\alph{enumi}.}
  \tightlist
  \item
    O*Net - comprehensive
  \end{enumerate}
\end{itemize}

@@

While we have accumulated a vast literature on how job demands and resources relate to and influence key organizational outcomes, recent work has called into question some of our basic assumptions regarding the experience of demands in particular. We build on the work of a small, but growing number of researchers who argue that the work elements may be appraised simultaneously as resources and demands (Webster et al., 2011) or that appraisals may change over time (Rosen et al., 2020), with primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) \emph{are there characteristics that are more likely to vary across demand and resource}, and 3) explore whether these subjective appraisals are differentially related to positive and negative outcomes. We utilize the O*Net database (\url{https://www.onetcenter.org/content.html}), which is the primary source of occupational information in the US, and as such, provides a rich source of information about occupational requirements (i.e., work activities and context) that may be rated in terms of level of demand or resource. We will refer to these as elements of working conditions throughout this paper (e.g., personal, contextual, or task-related conditions or elements of one's work).

\hypertarget{the-job-demands-resources-theory-and-challenge-hindrance-stressor-framework}{%
\subsection{The Job Demands-Resources Theory and Challenge-hindrance Stressor Framework}\label{the-job-demands-resources-theory-and-challenge-hindrance-stressor-framework}}

Two related theories serve as the foundation for the current study: Demerouti et al. (2001)'s job demands-resources theory and Cavanaugh et al. (2000)'s later challenge-hindrance stressor framework. The job demands-resources model Demerouti et al. (2001), Bakker and Demerouti (2017) highlights the importance of work characteristics on the experience of motivation and strain as well as other, more distal outcomes. The job demands-resources theory distinguishes between resources and demands. \emph{Resources} include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001). In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is commonly cited as a demand; Demerouti et al. (2001)). The perception of an element of one's job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; Bakker and Demerouti (2014)).

In response to inconsistent findings regarding demands and outcomes, Cavanaugh et al. (2000) expanded the job demands-resources theory in proposing the challenge-hindrance stressor framework, which draws from Lazarus and Folkman (1984)'s work on stress and coping. The challenge-hindrance stressor framework distinguishes between \emph{two forms of demands} -- \emph{challenges} and \emph{hindrances}. Both are considered stressors (e.g., Cavanaugh et al., 2000). Challenge demands promote mastery, personal growth, and future gains -- these stressors should lead to coping strategies that facilitate achievement. Work characteristics consistent with this definition include time pressure and responsibility. Hindrance demands, in contrast, inhibit growth, learning and goal achievement. Hindrance stressors in a work context include role conflict, role ambiguity, and organizational politics.

The original work on this topic suggests that challenge stressors are typically associated with positive outcomes and hindrance stressors are associated with negative outcomes (e.g., Cavanaugh et al., 2000). Meta-analytic explorations of this the challenge-hindrance stressor framework have generally been supportive of the framework's propositions (e.g., performance; (J. A. LePine et al., 2005) and engagement, (Crawford et al., 2010)). M. A. LePine (2022) explain the mechanisms by which demands are related to performance and wellbeing outcomes. First, stressors appraised as challenges typically result in a challenge appraisal, and engagement is likely to happen as a result. Engagement, in turn, is positively related to motivation, performance, growth, and wellbeing. Of note is that this energy may be depleted eventually, leading to strain. Stressors appraised as hindrances elicit a different process. Disengagement is likely to result from a hindrance appraisal, which in contrast, negatively impacts motivation, performance, growth and wellbeing. This happens because resources are depleted via frustrations and other affectively negative reactions (M. A. LePine, 2022). Recent work affirms this appraisal process. Pindek et al. (2024) meta-analyzed diary studies of dynamic stressors (i.e., short-term daily experiences of stressors) and concluded that daily challenge stressors had a postive direct association with performance, but a negative indirect association with performance through strain (as described by M. A. LePine (2022) above). As expected, hindrance stressors had both a direct and indirect (through strain) association with performance (Pindek et al., 2024).

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  jou,mask]{apa7}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\abstract{%
Much of our understanding of job demands and resources rests on an assumption that some aspects of jobs are resources and some are demands. This study documents the degree of variability in subjective ratings of job characteristics with respect to interpretation as resource and demand. Next, we quantify the degree to which perceptions match the literature-implicated resources/demands of job characteristics and also document associations with stress, burnout, and engagement. Job characteristics were not commonly categorized as solely resource or demand. Rather, job resources were also frequently viewed as challenging demands. OUTCOME VARIABLE INFORMATION HERE. These findings have implications for job design and administration particularly with regard to resource-laden elements that may also be experienced as demanding.
}

@@

I. Challenge-hindrance framework
+ Cavanaugh (\textasciitilde2000)
+ Last 20 years' research (variance - look at Pindek et al, 2024)
+ Appraisals \footnote{Ignore JD theory terminology - only talk about JDR \emph{model}, otherwise the verbage becomes confused (4/6/24)}

\begin{enumerate}
\def\labelenumi{\Roman{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  Antecedents (job elements)
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\alph{enumi}.}
\tightlist
\item
  O*Net - comprehensive
\end{enumerate}

@@

While we have accumulated a vast literature on how job demands and resources relate to and influence key organizational outcomes, recent work has called into question some of our basic assumptions regarding the experience of demands in particular. We build on the work of a small, but growing number of researchers who argue that work elements may be appraised simultaneously as resources and demands (Webster et al., 2011) or that appraisals may change over time (Rosen et al., 2020). Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) some characteristics are more likely than others to vary across demand and resource, and 3) subjective appraisals are differentially related to positive and negative outcomes. To illuminate these questions, we consult the \href{https://www.onetcenter.org/content.html}{O*Net database}, which provides a rich source of information about occupational requirements (i.e., work activities and context). We retain O*Net terminology of working condition elements throughout this paper (e.g., personal, contextual, or task-related conditions or elements of one's work).

\hypertarget{the-job-demands-resources-theory-and-challenge-hindrance-stressor-framework}{%
\subsection{The Job Demands-Resources Theory and Challenge-Hindrance Stressor Framework}\label{the-job-demands-resources-theory-and-challenge-hindrance-stressor-framework}}

Two related theories serve as the foundation for the current study: Demerouti et al. (2001)'s job demands-resources theory and Cavanaugh et al. (2000)'s challenge-hindrance stressor framework. The job demands-resources model (Demerouti et al., 2001) highlights the importance of demands and resources on the experience of motivation and strain as well as other, more distal outcomes. \emph{Resources} include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001). In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is commonly cited as a demand; Demerouti et al. (2001)). The perception of an element of one's job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; Bakker and Demerouti (2014)).

In response to inconsistent findings regarding demanding work characteristics and outcomes, Cavanaugh et al. (2000) proposed a challenge-hindrance stressor framework, which draws from Lazarus and Folkman (1984)'s perspective on stress and coping. The challenge-hindrance stressor framework distinguishes between \emph{two forms} of demands -- \emph{challenges} and \emph{hindrances}. Both are considered stressors (e.g., Cavanaugh et al., 2000). Challenge demands promote mastery, personal growth, and future gains -- these stressors should lead to coping strategies that facilitate achievement. Work characteristics consistent with this definition include time pressure and responsibility. Hindrance demands, in contrast, inhibit growth, learning and goal achievement. Hindrance stressors in a work context include role conflict, role ambiguity, and organizational politics.

The original work on this topic suggests that challenge stressors are typically associated with positive outcomes and hindrance stressors are associated with negative outcomes (e.g., Cavanaugh et al., 2000). Meta-analytic explorations of this the challenge-hindrance stressor framework have generally been supportive of the framework's propositions (e.g., performance; (J. A. LePine et al., 2005) and engagement, (Crawford et al., 2010)). M. A. LePine (2022) explain the mechanisms by which demands are related to performance and wellbeing outcomes.

First, stressors appraised as challenges typically result in a challenge appraisal, and engagement is likely to happen as a result. Engagement, in turn, is positively related to motivation, performance, growth, and wellbeing. Of note is that this energy may be depleted eventually, leading to strain. Stressors appraised as hindrances elicit a different process. Disengagement is likely to result from a hindrance appraisal, which in contrast, negatively impacts motivation, performance, growth and wellbeing. This happens because resources are depleted via frustrations and other affectively negative reactions (M. A. LePine, 2022). Recent work affirms this appraisal process. Pindek et al. (2024) meta-analyzed diary studies of dynamic stressors (i.e., short-term daily experiences of stressors) and concluded that daily challenge stressors had a postive direct association with performance, but a negative indirect association with performance through strain (as described by M. A. LePine (2022) above). As expected, hindrance stressors had both a direct and indirect (through strain) association with performance (Pindek et al., 2024).
